Learning constraints in spreadsheets and tabular data

### 2016-09-23 Paper/ECAI/tabular.tex
Rerun numbers

{\setlength{\tabcolsep}{0.33em}
\begin{table}[]
  \centering
  \caption{Summary of properties and results per spreadsheet category}
  \label{tbl:category_overview}
  \begin{tabular}{lccccccc}
 & \multicolumn{2}{c}{\textbf{Exercises} (9)} & \multicolumn{2}{c}{\textbf{Tutorials} (21)} & \multicolumn{2}{c}{\textbf{Data} (4)} \\
 & Overall & Sheet avg & Overall & Sheet avg & Overall & Sheet avg \\ \hline
    \textbf{Tables} & 19 & 2.11 & 48 & 2.29 & 4 & 1 \\ \hline
    \textbf{Cells} & 1231 & 137 & 1889 & 90 & 2320 & 580 \\ \hline
    \textbf{\begin{tabular}[c]{@{}l@{}}Intended\\[-4.5pt] Constraints\end{tabular}} & 34 & 3.78 & 52 & 2.48 & 6 & 1.50 \\ \hline \hline
\textbf{Recall} & 0.85 & 0.83 & 0.88 & 0.87 & 1.00 & 1.00 \\ \hline
\textbf{\begin{tabular}[c]{@{}l@{}}Recall\\[-4.5pt] Supported\end{tabular}} & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ \hline
\textbf{Precision} & 0.94 & 0.96 & 0.70 & 0.91 & 1.00 & 1.00 \\ \hline
\textbf{Runtime (s)} & 1.62 & 0.18 & 1.76 & 0.08 & 0.81 & 0.20
\end{tabular}
\end{table}}

\paragraph{Q1: Effectiveness}
Our first questions, Q1, is about the inability to find intended constraints due to excessive runtime. As Table~\ref{tbl:category_overview} (last row) shows, the runtime of our method on these spreadsheets is always fast.  
The average runtime across all spreadsheets is $0.13s$.
Across categories the average running times fluctuate in the range between $0.08s$ to $0.20s$.
While most spreadsheets can be processed very quickly, running times can go up to around $0.85s$ for others.
In the previous section we analyzed the effect of various factors that can help explain runtime behavior.
Our benchmark experiments show that our algorithm is able to perform well in practice, even for larger spreadsheets.

@@

Looking at the runtime per constraint template individually, the slowest by far is fuzzy lookup using $\pm 21\%$ of the running time.
It is followed by product ($\pm 7\%$), relative difference ($\pm 6\%$), running total ($\pm 5\%$), difference ($\pm 5\%$) and various row-aggregates (each $5\% - 3\%$).

Our method uses dependencies to increase efficiency by finding constraints incrementally. To illustrate the effect this can have, we ran the benchmarks using FOREIGNKEY instead of ALLDIFFERENT as base constraint to find conditional aggregates such as SUMIF. This is a stronger assumption, and a too strong in practice as not all keys have to be used in the conditions. However, the total running times per category are decreased by 6\% (exercises), 30\% (tutorials) and~3\% (data). This shows that the use of dependencies can have a strong effect on running times by sharing the computation and pruning done for one constraint with another.\sam{Check numbers} % (0.83 + 1.03 + 0.99) = 2.85 / (1.34 + 1.46 + 0.46) = 3.3  / (0.99 + 0.98 + 0.44) = 2.41

@@

\paragraph{Q2: Intended and supported constraints}
%\item Q2: it may fail to find intended constraints because it does not support such constraints; how does or method perform on real spreadsheets?
The overall recall achieved by \sname is~$0.88~(81/92)$.
When looking at the recall per category, \sname is able to consistently obtain high values for both overall and average recall, as shown in Table~\ref{tbl:category_overview}.
The intended constraints not discovered correspond to constraints that are not supported by the system (supported recall is 1).
Therefore, \sname is able to find all constraints for supported constraint templates, which confirms that our bias (signature) is not too restrictive.

>>>>

{\setlength{\tabcolsep}{0.33em}
\begin{table}[]
  \centering
  \caption{Summary of properties and results per spreadsheet category}
  \label{tbl:category_overview}
  \begin{tabular}{lccccccc}
 & \multicolumn{2}{c}{\textbf{Exercises} (9)} & \multicolumn{2}{c}{\textbf{Tutorials} (21)} & \multicolumn{2}{c}{\textbf{Data} (4)} \\
 & Overall & Sheet avg & Overall & Sheet avg & Overall & Sheet avg \\ \hline
    \textbf{Tables} & 19 & 2.11 & 48 & 2.29 & 4 & 1 \\ \hline
    \textbf{Cells} & 1231 & 137 & 1889 & 90 & 2320 & 580 \\ \hline
    \textbf{\begin{tabular}[c]{@{}l@{}}Intended\\[-4.5pt] Constraints\end{tabular}} & 34 & 3.78 & 52 & 2.48 & 6 & 1.50 \\ \hline \hline
\textbf{Recall} & 0.88 & 0.85 & 0.88 & 0.87 & 1.00 & 1.00 \\ \hline
\textbf{\begin{tabular}[c]{@{}l@{}}Recall\\[-4.5pt] Supported\end{tabular}} & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ \hline
\textbf{Precision} & 0.94 & 0.96 & 0.70 & 0.91 & 1.00 & 1.00 \\ \hline
\textbf{Runtime (s)} & 0.93 & 0.10 & 0.93 & 0.04 & 0.79 & 0.20
\end{tabular}
\end{table}}

\paragraph{Q1: Effectiveness}
Our first questions, Q1, is about the inability to find intended constraints due to excessive runtime. As Table~\ref{tbl:category_overview} (last row) shows, the runtime of our method on these spreadsheets is always fast.  
The average runtime across all spreadsheets is $0.08s$.
Across categories the average running times fluctuate in the range between $0.04s$ to $0.20s$.
While most spreadsheets can be processed very quickly, running times can go up to around $0.65s$ for others.
In the previous section we analyzed the effect of various factors that can help explain runtime behavior.
Our benchmark experiments show that our algorithm is able to perform well in practice, even for larger spreadsheets.

@@

Looking at the runtime per constraint template individually, the slowest by far is fuzzy lookup using $\pm 21\%$ of the running time.
It is followed by product ($\pm 7\%$), relative difference ($\pm 6\%$), running total ($\pm 5\%$), difference ($\pm 5\%$) and various row-aggregates ($\pm 5\%$).

Our method uses dependencies to increase efficiency by finding constraints incrementally. To illustrate the effect this can have, we ran the benchmarks without using \textit{ORDERED} as base constraint for fuzzy lookup.
The total running times per category increase by 74\% (exercises), 84\% (tutorials) and~13\% (data).
This shows that the use of dependencies can have a strong effect on running times by sharing the computation and pruning done for one constraint with another.
 % (0.83 + 1.03 + 0.99) = 2.85 / (1.34 + 1.46 + 0.46) = 3.3  / (0.99 + 0.98 + 0.44) = 2.41

@@

\paragraph{Q2: Intended and supported constraints}
%\item Q2: it may fail to find intended constraints because it does not support such constraints; how does or method perform on real spreadsheets?
The overall recall achieved by our system, \sname, is~$0.88~(81/92)$.
When looking at the recall per category, \sname is able to consistently obtain high values for both overall and average recall, as shown in Table~\ref{tbl:category_overview}.
The intended constraints not discovered correspond to constraints that are not supported by the system (supported recall is 1).
Therefore, \sname is able to find all constraints for supported constraint templates, which confirms that our bias (signature) is not too restrictive.
